---
title: "Data Analysis: Audit survey"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r packages, include=FALSE}

# load packages
library(stats)
library(janitor)
library(knitr)
library(scales)
library(arsenal)
library(table1)

```

### Data

```{r data, echo = FALSE}
load(file = "analytic_sample.Rda")

kable(head(analytic_sample))

```


### Descriptive characteristics

-------------------------------------------------------------



#### Pharmacy characteristics

Independent vs. chain pharmacies


```{r, echo = FALSE}
tabyl(analytic_sample, pharmtype)

# Do we see a meaningful difference between the prevalence of independent vs. chain pharmacies in sample?

chi_pharmtype <- chisq.test(x = table(analytic_sample$pharmtype))

chi_pharmtype

```


#### County characteristics in which pharmacies are located

##### Mean of median incomes in county 
* **Mean**: `r format(mean(analytic_sample$median_income), scientific=FALSE)`  
* **SD**:  `r format(sd(analytic_sample$median_income), scientific=FALSE)`

##### Population in county
* **Mean**: `r format(mean(analytic_sample$total_pop), scientific=FALSE)`  
* **SD**:   `r format(sd(analytic_sample$total_pop), scientific=FALSE)`

##### Percent White non-Hispanic residents in county
* **Mean**: `r percent(mean(analytic_sample$pct_white), accuracy=.1)`  
* **SD**:   `r percent(sd(analytic_sample$pct_white), accuracy=.1)`

##### Percent residents in county 65+
* **Mean**: `r percent(mean(analytic_sample$prop_65plus), accuracy=.1)`  
* **SD**:   `r percent(sd(analytic_sample$prop_65plus), accuracy=.1)`  

##### Time to reach pharmacist in seconds

* **Mean**: `r round(mean(analytic_sample$waittime_sec, na.rm=TRUE), 1)` seconds
* **SD**: `r round(sd(analytic_sample$waittime_sec, na.rm = TRUE), 1)`
* **Number of missing time values**: `r sum(is.na(analytic_sample$waittime_sec))`  

--------------------------------------------------------------------  

### Summary of survey responses  


```{r, results='asis', echo=FALSE}
tab2 <- tableby(pharmtype ~ shing_avail + flu_avail + hdflu_avail, data=analytic_sample)

summary(tab2, text=TRUE)

```


### Chi-square tests comparing dichotomous outcome (yes/no)

--------------------------------------------------------------------


#### Shingles vaccine availability

```{r, results='asis'}
tab1 <- tableby(shing_avail ~ pharmtype + nchs_code, data=analytic_sample)

summary(tab1, text=TRUE)

```

Is there a relationship between pharmacy type and shingles availability?

``` {r, echo = FALSE}
table(analytic_sample$pharmtype,
      analytic_sample$shing_avail)

chi_shing <- chisq.test(x = table(analytic_sample$pharmtype,
                                analytic_sample$shing_avail))

chi_shing
```



#### Regular flu vaccine availability

Is there a relationship between **pharmacy type** and regular-dose flu availability?
```{r, echo = FALSE}
table(analytic_sample$pharmtype,
      analytic_sample$flu_avail)

chi_flu <- chisq.test(x = table(analytic_sample$pharmtype,
                                  analytic_sample$flu_avail))

chi_flu

```



#### High-dose flu vaccine availability

Is there a relationship between **pharmacy type** and hd flu availability?

``` {r, echo = FALSE}
table(analytic_sample$pharmtype,
      analytic_sample$hdflu_avail)

chi_hdflu <- chisq.test(x = table(analytic_sample$pharmtype,                analytic_sample$hdflu_avail))

chi_hdflu
```


Is there a relationship between **rurality** and hd flu availability?
```{r}
table(analytic_sample$nchs_code,
      analytic_sample$hdflu_avail)

chi_rural <- chisq.test(x = table(analytic_sample$nchs_code,
                                analytic_sample$hdflu_avail))

chi_rural
```


#### Table 1

```{r, echo=FALSE}

table1(~ pharmtype + region + total_pop, data = analytic_sample)


table1(~ shing_avail + flu_avail + hdflu_avail | pharmtype, data = analytic_sample)

```
