---
title: "Tables - Aim 1: Audit Survey of Pharmacy Vaccine Availability"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r packages, include=FALSE}

# load packages
library(stats)
library(janitor)
library(knitr)
library(scales)
library(arsenal)
library(table1)
library(sjPlot)
library(tidyverse)

```


```{r data, echo = FALSE}
load(file = "analytic_sample.Rda")

analytic_sample <- analytic_sample %>%
  mutate(pct_white = pct_white * 100) %>%
  mutate(prop_65plus = prop_65plus *100)
  


```

\

## DESCRIPTIVE CHARACTERISTICS ----

#### TABLE 1. Descriptive statistics of counties in analytic sample of 384 pharmacies 

```{r, echo=FALSE}

label(analytic_sample$pharmtype) <- "Pharmacy type"
label(analytic_sample$median_income) <- "Median income, $"
label(analytic_sample$pct_white) <- "% White non-Hispanic population"
label(analytic_sample$total_pop) <- "Total population"
label(analytic_sample$waittime_sec) <- "Wait time (seconds)"
label(analytic_sample$prop_65plus) <- "% of county population 65+"

analytic_sample$metro <-
  factor(analytic_sample$metro)
label(analytic_sample$region) <- "Region"


analytic_sample$metro <-
  factor(analytic_sample$metro,
         levels=c(1,0),
         labels=c("Metropolitan area",
                  "Non-metropolitan area"))
label(analytic_sample$metro) <- "Metro area"


table1(~ region + metro + median_income + pct_white + total_pop + prop_65plus + waittime_sec | pharmtype, data = analytic_sample)

table1(~ pharmtype | region, data = analytic_sample)
table1(~ pharmtype | metro, data = analytic_sample)



```
\
\
\
\


#### TABLE 2a. Summary of availability of vaccines at chain vs. independent pharmacies 

```{r, echo=FALSE}

# shingles


analytic_sample$shing_avail <-
  factor(analytic_sample$shing_avail,
         levels=c(1,0),
         labels=c("Available",
                  "Unavailable"))

label(analytic_sample$shing_avail) <- "Shingles vaccine"

# flu

analytic_sample$flu_avail <-
  factor(analytic_sample$flu_avail,
         levels=c(1,0),
         labels=c("Available",
                  "Unavailable"))

label(analytic_sample$flu_avail) <- "Regular flu vaccine"

# hd flu

analytic_sample$hdflu_avail <-
  factor(analytic_sample$hdflu_avail,
         levels=c(1,0),
         labels=c("Available",
                  "Unavailable"))

label(analytic_sample$hdflu_avail) <- "65+ flu vaccine"

table1(~ shing_avail + flu_avail + hdflu_avail | pharmtype, data = analytic_sample)


test_shing <- chisq.test(table(analytic_sample$pharmtype, analytic_sample$shing_avail))
test_shing

test_shing$statistic
test_shing$p.value

```
\
\
\
\

#### TABLE 2b. Chi-square test of differences in availability of vaccines at chain vs. independent pharmacies 

```{r, echo=FALSE}

pvalue <- function(x, ...) {
    # Construct vectors of data y, and groups (strata) g
    y <- unlist(x)
    g <- factor(rep(1:length(x), times=sapply(x, length)))
    if (is.numeric(y)) {
        # For numeric variables, perform a standard 2-sample t-test
        p <- t.test(y ~ g)$p.value
    } else {
        # For categorical variables, perform a chi-squared test of independence
        p <- chisq.test(table(y, g))$p.value
    }
    # Format the p-value, using an HTML entity for the less-than sign.
    # The initial empty string places the output on the line below the variable label.
    c("", sub("<", "&lt;", format.pval(p, digits=3, eps=0.001)))
}

table1(~ shing_avail + flu_avail + hdflu_avail | pharmtype,
    data=analytic_sample, overall=F, extra.col=list(`P-value`=pvalue))

```
\
\
\
\

## CHI-SQUARE TESTS: ALL VARIABLES 
\

#### APPENDIX C. Chi-square tests and t-tests for all variables correlated with shingles vaccine availability

```{r, echo=FALSE, warning=FALSE}

pvalue <- function(x, ...) {
    # Construct vectors of data y, and groups (strata) g
    y <- unlist(x)
    g <- factor(rep(1:length(x), times=sapply(x, length)))
    if (is.numeric(y)) {
        # For numeric variables, perform a standard 2-sample t-test
        p <- t.test(y ~ g)$p.value
    } else {
        # For categorical variables, perform a chi-squared test of independence
        p <- chisq.test(table(y, g))$p.value
    }
    # Format the p-value, using an HTML entity for the less-than sign.
    # The initial empty string places the output on the line below the variable label.
    c("", sub("<", "&lt;", format.pval(p, digits=3, eps=0.001)))
}

table1(~ pharmtype + region + metro + median_income + pct_white + total_pop + prop_65plus | shing_avail,
    data=analytic_sample, overall=F, extra.col=list(`P-value`=pvalue))

```
\
```{r, echo=FALSE}

table1(~ shing_avail | pharmtype, data = analytic_sample)
table1(~ shing_avail | region, data = analytic_sample)
table1(~ shing_avail | metro, data = analytic_sample)
```
\
\
\

#### APPENDIX D. Chi-square tests and t-tests for all variables correlated with regular flu vaccine availability

```{r, echo=FALSE}

table1(~ pharmtype + region + median_income + pct_white + total_pop + prop_65plus | flu_avail,
    data=analytic_sample, overall=F, extra.col=list(`P-value`=pvalue))

```
\
```{r, echo=FALSE}

table1(~ flu_avail | pharmtype, data = analytic_sample)
table1(~ flu_avail | region, data = analytic_sample)
table1(~ flu_avail | metro, data = analytic_sample)
```
\
\

#### APPENDIX E. Chi-square tests and t-tests: senior flu vaccine availability

```{r, echo=FALSE}

table1(~ pharmtype + region + median_income + pct_white + total_pop + prop_65plus | hdflu_avail,
    data=analytic_sample, overall=F, extra.col=list(`P-value`=pvalue))

```
\
```{r, echo=FALSE}

table1(~ hdflu_avail | pharmtype, data = analytic_sample)
table1(~ hdflu_avail | region, data = analytic_sample)
table1(~ hdflu_avail | metro, data = analytic_sample)
```
\
\
\

## LOGISTIC REGRESSIONS
\

#### Appendix F. Logistic regression coefficients: shingles availability

```{r, echo=FALSE}


logit_shing <- glm(shing_avail ~  pharmtype  + region + metro+ median_income + pct_white + total_pop +prop_65plus, data = analytic_sample, family = "binomial")

tab_model(logit_shing)

```
\
\
\
\

#### Appendix G. Logistic regression coefficients: regular flu availability

```{r, echo=FALSE}


logit_flu <- glm(flu_avail ~  pharmtype  + region + metro+ median_income + pct_white + total_pop +prop_65plus, data = analytic_sample, family = "binomial")

tab_model(logit_flu)

```
\
\
\
\

#### Appendix H. Logistic regression coefficients: 65+ flu availability

```{r, echo=FALSE}


logit_hdflu <- glm(hdflu_avail ~  pharmtype  + region + metro+ median_income + pct_white + total_pop +prop_65plus, data = analytic_sample, family = "binomial")

tab_model(logit_hdflu)

```
\
\
\
\


#### Quick summary stats of county-level variables for pharmacies

##### Mean of median incomes in county 
* **Mean**: `r format(mean(analytic_sample$median_income), scientific=FALSE)`  
* **SD**:  `r format(sd(analytic_sample$median_income), scientific=FALSE)`

##### Population in county
* **Mean**: `r format(mean(analytic_sample$total_pop), scientific=FALSE)`  
* **SD**:   `r format(sd(analytic_sample$total_pop), scientific=FALSE)`

##### Percent White non-Hispanic residents in county
* **Mean**: `r percent(mean(analytic_sample$pct_white), accuracy=.1)`  
* **SD**:   `r percent(sd(analytic_sample$pct_white), accuracy=.1)`

##### Percent residents in county 65+
* **Mean**: `r percent(mean(analytic_sample$prop_65plus), accuracy=.1)`  
* **SD**:   `r percent(sd(analytic_sample$prop_65plus), accuracy=.1)`  

##### Time to reach pharmacist in seconds

* **Mean**: `r round(mean(analytic_sample$waittime_sec, na.rm=TRUE), 1)` seconds
* **SD**: `r round(sd(analytic_sample$waittime_sec, na.rm = TRUE), 1)`
* **Number of missing time values**: `r sum(is.na(analytic_sample$waittime_sec))`


#### Resources:
* https://cran.r-project.org/web/packages/table1/vignettes/table1-examples.html 
* https://cran.r-project.org/web/packages/gtsummary/vignettes/inline_text.html
* https://cran.r-project.org/web/packages/sjPlot/vignettes/tab_model_estimates.html
* https://statsandr.com/blog/chi-square-test-of-independence-in-r/#chi-square-test-of-independence-in-r
* https://cran.r-project.org/web/packages/arsenal/vignettes/tableby.html
